
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Daniel Firebanks - Based off of "Deedy - One Page Two Column Resume"
% LaTeX Template
% - Added commands for links and information at the top bar + icons
% - Changed color, spacing and placement of dates/position
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{dafirebanks-resume-openfont}

\usepackage{ragged2e}

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Daniel}{Firebanks-Quevedo}{
\git{http://github.com/thefirebanks}{thefirebanks} | \email{dfireban@oberlin.edu}{dfireban@oberlin.edu} | 
\phone{202-294-9862} | \linkedin{https://www.linkedin.com/in/firebanks}{firebanks}
}

%\headerbro{John}{Smith}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} \vspace{-3pt}
{\color{blue}\hrule width 88pt}\vspace{5pt}
\subsection{B.A in Computer Science}
\descript{Oberlin College}\\
\location{Expected May 2020 | Oberlin, OH}
Minor in \underline{Mathematics} \\ 
\location{ GPA: 3.54/ 4.0}

\subsection{\\Computer Science Study Abroad}
\descript{University of Technology and Economics  (BME)}\\
\location{Jan-May 2019 | Budapest, Hungary}

\subsection{\\International Baccalaureate}
\descript{United World College USA\\}
\location{May 2016 | Montezuma, NM}\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\vspace{-3pt}
{\color{blue}\hrule width 45pt} \vspace{5pt}
\subsection{Programming}
\location{Comfortable:}
 Python \textbullet{} Java \textbullet{} C++ \\ \textbullet{} Javascript \textbullet{} Scheme
\textbullet{} \LaTeX \\ \sectionsep
\location{Familiar:}
 C \textbullet{} C\# \textbullet{} R %\textbullet{} Node.js/React.js \\ 
 \textbullet{} Shell \textbullet{} SQL \\
\sectionsep 
\subsection{Languages}
Spanish (Native) \textbullet{} English (Proficient) \\
\textbullet{} French \textbullet{} Hungarian (Conversational)
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\vspace{-3pt}
{\color{blue} \hrule width 107pt} \vspace{5pt}
%\subsection{Undergraduate}
Advanced Algorithms \\
Economics and Computation \\
Computational Biology and Medicine \\
Data Science\\
Complex Networks \\
Linear Algebra \\ 
Multivariable Calculus \\
 \\ 
Systems Programming \\

% % \sectionsep
% \subsection{\\Online}
% Machine Learning\\
% Game Theory\\
% %Web Application Development\\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\vspace{-3pt}
{\color{blue}\hrule width 78pt \vspace{5pt}}
Jazz/Classical Guitar \textbullet{} Percussion\\
\textbullet{} Stand-up comedy
\textbullet{} Photography\\ 
\textbullet{} Close-up Magic
\textbullet{} Latin and Ballroom Dancing \textbullet{} Cognitive Neuroscience\\
\textbullet{} Cooking 
\textbullet{} Behavioral/Development Economics  
\textbullet{} Outdoor recreation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.2pt}
\section{Experience}
\vspace{-3pt}
{\color{blue}\hrule} \vspace{5pt}
\runsubsection{Economic Analysis (Data Science) Intern} 
\hspace{40pt} \location{Jun 2018 - Aug 2018}
%\newline
\descript{Public Company Accounting Oversight Board} 
%\hspace{30pt} 
%\newline
\location{}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Trained a Conditional Random Fields (CRF) machine learning model to identify structure and extract text from accounting statements.
	\item Built tools that automated cleaning, merging, and query-based retrieval of financial/accounting data for text analysis and risk prediction.
	\item Wrote a parser in C\# to extract text while maintaining logical structure from non-standardized HTML documents, increasing accuracy from 47\% to 78\%.
\end{tightemize}
% \vspace{1pt}
\sectionsep

\runsubsection{Computer Science Teaching Assistant} 
\hspace{54pt}
\location{Aug 2017 - Dec 2018}
\descript{Oberlin College} \location{} 
\begin{tightemize}
	\item Engaged in weekly lab tutoring sessions for groups of 20-25 students, by assisting them in developing software design proficiency, identifying/resolving bugs, and peer programming. 
	\item Classes: \textit{Introduction to CS, Data Structures and Systems Programming.}
\end{tightemize}
\sectionsep

\runsubsection{Technology Consultant}
\hspace{127pt}
\location{Jan 2017 - Dec 2018}
\descript{Oberlin College}
\location{}
\begin{tightemize}
	\item Provided first-level client services/support to students, faculty and staff by diagnosing software issues and formulating solutions to them. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\vspace{-3pt}
{\color{blue}\hrule} \vspace{5pt}
%\runsubsection{Computer Science Department,} \location{Oberlin College}
%\runsubsection{Research Assistant} | \underline{\textit{Self-interested multi-agent reasoning in complex systems}}\\
\runsubsection{Self-interested multi-agent reasoning in complex systems} \\
\descript{Research Assistant, Oberlin College}
\hspace{70pt} \location{Aug 2017 – Dec 2018}
\begin{tightemize}
	\item Studied multi-agent systems and reinforcement learning algorithms applied to StarCraft2 (SC2) with professor \textbf{\href{http://www.cs.oberlin.edu/~aeck/}{Adam Eck}}.  
	\item Built basic bots for the test environments provided by DeepMind.
	\item Created a framework to build intelligent bots through the Python (PySC2) and Java SC2 APIs that uses the Raw Interface of the game. 
\end{tightemize}
\sectionsep

%\descript{Lead Researcher} | \underline{\textit{Ensemble Learning for Offensive Language Detection in Tweets}}
\runsubsection{Ensemble Learning for Offensive Language Detection in Tweets}\\
\descript{Lead Researcher, Oberlin College} 
\hspace{81pt} \location{Aug 2017 –  Dec 2018}
\begin{tightemize}
	\item Built an ensemble learning model to classify hate-speech and offensive language in tweets, composed of:
	\vspace{\topsep}
	\begin{tightemize}
		\item A Bayesian structure, an LSTM Recurrent Neural Network and a Voting Classifier module based on word embeddings and a lexicon frequency score. 
	\end{tightemize}\vspace{\topsep}
	\item Designed and implemented a weighted voting system for the outcomes of the methods mentioned above.
	\item Wrote a curricular unit in algorithmic bias for the Machine Learning class.
\end{tightemize}
\sectionsep


% THESE ARE THE ONES THAT ARE MOVEABLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\descript{Summer Researcher} | \underline{\textit{Sentiment Analysis of Viral Tweets}}\\
\runsubsection{Sentiment Analysis of Viral Tweets}\\
\descript{Summer Researcher, Oberlin College}
\hspace{75pt}\location{Jun 2017 – Jul 2017}
\begin{tightemize}
	\item Analyzed 300,000 tweets from a large group of scientists for changes in sentiment and its possible effects on virality. 
	\item Used Python and R to apply machine learning (Naive Bayes, SVM, Max. Ent) and natural language processing techniques.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES AND LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities and Leadership } 
\vspace{-3pt}
{\color{blue}\hrule} \vspace{5pt}
\begin{tabular}{rll}
\location{Nov 2017 - Present} 	& Computer Science Majors Committee (Member)\\
\location{Aug 2016 - Present}   & International Student Organization (President) 
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}
